---
title: "week 5 assignment"
author: "Hongtao Qian"
date: "2020/5/16"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

## 10.5.1: How can you tell if an object is a tibble? (Hint: try printing mtcars, which is a regular data frame).  
```{r}
print(mtcars)%>%
  .$"cyl"
```

## I think I can see the chart with columns and rows when I code "print()" and I can see a row if I want to extract the column through ".$".  

## 10.5.2: Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviours cause you frustration? 
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
df[, "xyz"]
df[, c("abc", "xyz")]
```
```{r}
tib<-tibble(abc=1, xyz="a")
tib[,"xyz"]
tib[,c("abc","xyz")]
```

## When I type "tib$x", I can only get the null consequence, so I delete this line and I also can get two meaningful diagrams. The only distinction is the formating of the consequence of the first diagram. Is it a vector for data.frame?  

## 10.5.4: Practice referring to non-syntactic names in the following data frame by:

Extracting the variable called 1.

Plotting a scatterplot of 1 vs 2.

Creating a new column called 3 which is 2 divided by 1.

Renaming the columns to one, two and three.  
```{r}
what<-tibble(`1`=1:10, `2`=`1`*2+rnorm(length(`1`)))%>%
  print()
what[["1"]]
ggplot(what)+
geom_point(mapping=aes(x =`1`,y =`2`))
what[["3"]]<-what$`2`/what$`1`
print(what)
```
```{r}
what <- rename(what, one = `1`, two = `2`, three = `3`)%>%
  print()
```

## I have a problem when I try to use the code "mutate" because I seem not to be allowed to "add the column" to the dataset through "mutate" but it really shows there is an extra column in the dataset. 
```{r}
mutate(what, `3`=two/one)
```

## 10.5.5: What does tibble::enframe() do? When might you use it?
```{r}
enframe(c(a=1, b=2, c=34, z=789))
```

## It can convert two equally long vectors into a tibble. 

## 11.2.2.1: What function would you use to read a file where fields were separated with “|”?

## I google this and I find it is for "read_delim()" but can you give an example about how to use it?  

## 11.2.2.4: Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By default, read_csv() assumes that the quoting character will be ". What argument to read_csv() do you need to specify to read the following text into a data frame? 
```{r}
read_csv("x,y\n1,'a,b'", quote="'")
```

##11.2.2.5: Identify what is wrong with each of the following inline CSV files. What happens when you run the code?  
```{r}
read_csv("a,b\n1,2,3\n4,5,6")
read_csv("a,b,c\n1,2\n1,2,3,4")
read_csv("a,b\n\"1")
read_csv("a,b\n1,2\na,b")
read_csv("a;b\n1;3")
```

## For the diagram one, there are three values for each row but only two columns, so the last column has disappeared.  
## For the diagram two, there are only two columns, so for the first vector row, the last missing one is filled with "NA"; for the second vector row, the last excessive one disappears.  
## For the diagram three, there are two columns but there is only one value in the vector row, so the missing value is filled with "NA".  
## For the diagram four, the value is the as the column name and there should be some problems with the value.  
## For the diagram five, the ";" is used instead of "," to separate different columns but this cannot be recognized as "," by the studio, so the tibble will have only one column and one row.  

## 11.3.5.1: What are the most important arguments to locale()?  
## I think it is absolutely important arguments for all types of data import (, but I think it is better to process the data in advance through "csv" document).  

## 11.3.5.2: What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to ","? What happens to the default value of decimal_mark when you set the grouping_mark to "."?

## It is an error. 
```{r}
locale(decimal_mark=",")
```

## It tends to let the period "." to be figured as grouping mark.   
```{r}
locale(grouping_mark = ",")
```

## It tends to lect the period "." to be digured as decimal mark. 

## 11.3.5.3: I didn’t discuss the date_format and time_format options to locale(). What do they do? Construct an example that shows when they might be useful.

## Sorry, I think I have no idea!!!!!!

## 11.3.5.7: Generate the correct format string to parse each of the following dates and times
```{r}
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"

parse_date(d1, "%B %d, %Y")
parse_date(d2, "%Y-%b-%d")
parse_date(d3, "%d-%b-%Y")
parse_date(d4, "%B %d (%Y)")
parse_date(d5, "%m/%d/%y")
parse_time(t1, "%H%M")
parse_time(t2, "%H:%M:%OS %p")
```



