---
title: "week 3 assignment"
author: "Hongtao Qian"
date: "2020/4/29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(nycflights13)
```

4.4.1:  
The name we have given a value is "my_variable", but the code I type to get the value is "my_varıable" which is "ı" instead of "i", (but how to type "ı"?).  

4.4.2:  
```{r}
library(tidyverse)
ggplot(data=mpg)+geom_point(mapping=aes(x=displ, y=hwy))
filter(mpg, cyl==8)
filter(diamonds, carat>3)
```

This is really tricky. The second code mistakes the "data" to "dota". The third code mistakes the "filter" to "fliter" and misses one "=". THe forth code misses "s" attached to the data name"diamaonds" and there are no dataset called "diamond".  

4.4.3:  
This tells the use of different shortcut key combination. It is quite useful. 

5.2.4.1:  
```{r}
filter(flights, arr_delay>=2)
filter(flights, month==7|month==8|month==9)
filter(flights, arr_delay>=2 & dep_delay==0)
filter(flights, (dep_time>0 & dep_time<=600) | dep_time==2400)
```

5.2.4.2:  
```{r}
filter(flights, between(month,7,9))
filter(flights, between(dep_time,0,600)|dep_time==2400)
```

Only the code for 2 and 4 can be modified by "between". 

5.2.4.3:  
```{r}
filter(flights, is.na(dep_time))
```

These flights should be cancelled ones due to lack of numerous variables on one row. 

5.3.1.1:  
```{r}
arrange(flights, desc(is.na(dep_time)))
```

5.3.1.2:  
```{r}
arrange(flights, desc(dep_delay))
arrange(flights, dep_delay)
```

5.3.1.3:  
I do not know how to accomplish it with arrange only. 

5.3.1.4:  
```{r}
arrange(flights, distance)
arrange(flights, desc(distance))
```

The first chart can help to find the shortest and the second one can help to find the farthest.  
5.4.1.1:  
```{r}
select(flights, dep_time,dep_delay:arr_time,arr_delay)
select(flights, dep_time, dep_delay,arr_time,arr_delay)
select(flights, starts_with("dep_"),starts_with("arr_"))
select(flights, contains("arr"),contains("dep"),-contains("sched"), -carrier)
```

5.4.1.2: 
```{r}
select(flights, year,year,month,day)
```

nothing happens. Why can you be so smart here??  

5.4.1.3:  
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
select(flights,one_of(vars))
```

This function helps to show all variables in the vector.  

5.4.1.4:  
```{r}
select(flights, contains("TIME"))
```

5.5.2.1:  
```{r}
transmute(flights, dep_time, dep_time_minute=(dep_time%/%100)*60+dep_time%%100, sched_dep_time, sched_dep_time_minute=(sched_dep_time%/%100)*60+sched_dep_time%%100)
```

5.5.2.2:  
```{r}
transmute(flights, air_time, time=arr_time-dep_time)
```

The time for "arr_time"-"dep_time" becomes very strange because the "air_time" is counting the minutes in the air while "arr_time" and "dep_time" have the other format of "hour-minute" whose direct calculation can lead to a mess. 

5.5.2.3:  
```{r}
select(flights, dep_time, sched_dep_time, dep_delay)
```

dep_delay=dep_time-sched_dep_time

5.5.2.4:  
```{r}
arrange(flights, desc(dep_delay))
```

I do not know how to use the function "mid_rank()" but I think I can get the same consequence by the "arrange()" function.  

5.5.2.5
```{r}
1:3+1:10
```

The error code??  

5.6.7.5:  
```{r}
not_cancelled<-flights %>%
  filter(!is.na(dep_delay),!is.na(arr_delay))
delays<-not_cancelled%>%
  group_by(carrier)%>%
  summarise(n=n(),delay=mean(arr_delay, na.rm = TRUE))%>%
  filter(n>=25)
ggplot(data=delays, mapping = aes(x=n, y=delay, color=carrier))+geom_point()

delays<-not_cancelled%>%
  group_by(dest)%>%
  summarise(n=n(),delay=mean(arr_delay, na.rm = TRUE))%>%
  filter(n>=25)
ggplot(data=delays, mapping = aes(x=n, y=delay, color=dest))+geom_point()
```

I get that the carrier F9 should have the worst delay. 